\textbf{NBA Party}

### 2017-07-15 cardinal_analytx_presentation/nightlife_and_sports.tex
Now including only the party variable(s) of interest in regression tables. Listing what we control for in a footnote.

\begin{frame}   \frametitle{Results: NBA}
  \vspace{-2pt}
  \centering
  \tiny{ % m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.557$^{***}$ &  \\    & (0.149) &  \\    & & \\   Party continuous &  & $-$0.158$^{*}$ \\    &  & (0.095) \\    & & \\   Lag changes in posession & 0.189 & 0.181 \\    & (0.140) & (0.140) \\    & & \\   Logged travel distance & $-$0.015 & $-$0.010 \\    & (0.026) & (0.026) \\    & & \\   East-west travel direction & $-$0.072 & $-$0.037 \\    & (0.234) & (0.234) \\    & & \\   Number hours rest time & 0.001 & 0.001 \\    & (0.001) & (0.001) \\    & & \\   Time of game during day & 0.006 & 0.004 \\    & (0.013) & (0.013) \\    & & \\   Home team effect & 0.002 & 0.004 \\    & (0.044) & (0.044) \\    & & \\   Logged travel distance * east-west & 0.011 & 0.007 \\    & (0.036) & (0.036) \\    & & \\  \hline \\[-1.8ex]  Observations & 9,517 & 9,517 \\  Log Likelihood & $-$6,586.320 & $-$6,592.159 \\  Akaike Inf. Crit. & 13,200.640 & 13,212.320 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  }   
\end{frame}

@@

\begin{frame}   \frametitle{Placebo test (discrete indicator): what if players rest?}
  \centering
  \tiny{ % mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.053 \\    & (0.084) \\    & \\   Lag changes in posession & 0.170 \\    & (0.140) \\    & \\   Logged travel distance & $-$0.004 \\    & (0.026) \\    & \\   East-west travel direction & $-$0.034 \\    & (0.235) \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & (0.001) \\    & \\   Time of game during day & 0.002 \\    & (0.013) \\    & \\   Home team effect & $-$0.006 \\    & (0.044) \\    & \\   Logged travel distance * east-west & 0.006 \\    & (0.036) \\    & \\   Constant & $-$0.865 \\    & (0.695) \\    & \\  \hline \\[-1.8ex]  Observations & 9,517 \\  Log Likelihood & $-$6,593.344 \\  Akaike Inf. Crit. & 13,214.690 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular} 
}
\end{frame}

@@

\begin{frame}   \frametitle{Results: MLB}
  \centering
  \tiny{ % m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.120$^{*}$ &  \\    & (0.071) &  \\    & & \\   Nightlife (no weekend interaction) &  & 0.137 \\    &  & (0.134) \\    & & \\   Bookmaker's odds & 2.682$^{***}$ & 2.669$^{***}$ \\    & (0.158) & (0.158) \\    & & \\   Home-team effect & 0.014 & 0.144 \\    & (0.034) & (0.102) \\    & & \\   Number of rest days & 0.018 & 0.016 \\    & (0.021) & (0.021) \\    & & \\   Logged travel distance & $-$0.005 & $-$0.003 \\    & (0.005) & (0.005) \\    & & \\   Weekend & 0.044 & 0.002 \\    & (0.038) & (0.029) \\    & & \\   Constant & $-$1.363$^{***}$ & $-$1.468$^{***}$ \\    & (0.084) & (0.122) \\    & & \\  \hline \\[-1.8ex]  Observations & 26,473 & 26,473 \\  Log Likelihood & $-$18,124.350 & $-$18,125.300 \\  Akaike Inf. Crit. & 36,272.700 & 36,264.600 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  }
\end{frame}

@@

\begin{frame}   \frametitle{Defense in the NBA is affected by our measure for party}
  \tiny{  % mpa1, tpa, tps
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & \multicolumn{2}{c}{Team Points Admitted} & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.970$^{***}$ &  &  \\    & (0.835) &  &  \\    & & & \\   Continuous party measure &  & 1.661$^{***}$ & $-$0.139 \\    &  & (0.644) & (0.637) \\    & & & \\   Lag change in possessions & 6.694$^{***}$ & 6.751$^{***}$ & 5.858$^{***}$ \\    & (0.973) & (0.973) & (0.963) \\    & & & \\   Logged travel distance & $-$0.114 & $-$0.132 & $-$0.285 \\    & (0.198) & (0.198) & (0.196) \\    & & & \\   Number hours since last game & 0.011$^{*}$ & 0.015$^{**}$ & 0.016$^{**}$ \\    & (0.006) & (0.007) & (0.007) \\    & & & \\   Home team effect & $-$3.269$^{***}$ & $-$3.269$^{***}$ & 2.417$^{***}$ \\    & (0.303) & (0.303) & (0.300) \\    & & & \\   Constant & 68.114$^{***}$ & 67.686$^{***}$ & 71.348$^{***}$ \\    & (4.805) & (4.810) & (4.758) \\    & & & \\  \hline \\[-1.8ex]  Observations & 6,234 & 6,234 & 6,234 \\  R$^{2}$ & 0.091 & 0.090 & 0.084 \\  Adjusted R$^{2}$ & 0.087 & 0.086 & 0.079 \\  Residual Std. Error (df = 6201) & 11.670 & 11.675 & 11.549 \\  F Statistic (df = 32; 6201) & 19.453$^{***}$ & 19.247$^{***}$ & 17.720$^{***}$ \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}    }
\end{frame}

@@

\begin{frame}   \frametitle{Future research - NBA}
  Within the NBA
  \begin{itemize}     
    \item Are teams more likely to party after a win or a       loss?
    \item Do teams who aren't going to make the playoffs party more?
    \item Are there demographic differences which influence propensity to party? E.g. are younger, unmarried players more susceptible to our treatment effect?
    \item We could also examine how shots taken vs. shots scored are affected for star players.
  \end{itemize}
  \vspace{12pt}  A preliminary and ad-hoc analysis shows that injury risk increases as a function of party.\footnote{We look for instances where players are put on the bench and stop playing (at least several) games as a function of our nightlife indicator.}
  This might inform coaches which players to bench and when.

\end{frame}

>>>>

\begin{frame}   \frametitle{Results: NBA\footnote{\tiny{We also account for: \texttt{Lag changes in posession, logged travel distance, east-west travel direction, number hours rest time, time of game during day, home team effect.}}}}
  \vspace{-2pt}
  \centering 
  % m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.557$^{***}$ &  \\    & (0.149) &  \\    & & \\   Party continuous &  & $-$0.158$^{*}$ \\    &  & (0.095) \\    & & \\  \hline \\[-1.8ex]  Observations & 9,517 & 9,517 \\  Log Likelihood & $-$6,586.320 & $-$6,592.159 \\  Akaike Inf. Crit. & 13,200.640 & 13,212.320 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{frame}

@@

\begin{frame}   \frametitle{Placebo test (discrete indicator): what if players rest?\footnote{\tiny{We also account for: \texttt{Lag changes in posession, logged travel distance, east-west travel direction, number hours rest time, time of game during day, home team effect.}}}}
  \centering
% mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.053 \\    & (0.084) \\    & \\  \hline \\[-1.8ex]  Observations & 9,517 \\  Log Likelihood & $-$6,593.344 \\  Akaike Inf. Crit. & 13,214.690 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{frame}

@@

\begin{frame}   \frametitle{Results: MLB\footnote{\tiny{We also account for \texttt{bookmaker's odds, home-team effect, number of rest days, logged travel distance, weekend indicator.}}}}
  \centering
% m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.120$^{*}$ &  \\    & (0.071) &  \\    & & \\   Nightlife (no weekend interaction) &  & 0.138 \\    &  & (0.135) \\    & & \\  \hline \\[-1.8ex]  Observations & 26,473 & 26,473 \\  Log Likelihood & $-$18,124.350 & $-$18,125.260 \\  Akaike Inf. Crit. & 36,272.700 & 36,274.510 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{frame}

@@

\begin{frame}   \frametitle{Defense in the NBA is affected by our measure for party\footnote{\tiny{We also account for \texttt{Lag changes in posession, logged travel distance, number of hours since last game, home team effect.}}}}
% mpa1, tpa, tps
\scriptsize{
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & \multicolumn{2}{c}{Team Points Admitted} & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.970$^{***}$ &  &  \\    & (0.835) &  &  \\    & & & \\   Continuous party measure &  & 1.661$^{***}$ & $-$0.139 \\    &  & (0.644) & (0.637) \\    & & & \\  \hline \\[-1.8ex]  Observations & 6,234 & 6,234 & 6,234 \\  R$^{2}$ & 0.091 & 0.090 & 0.084 \\  Adjusted R$^{2}$ & 0.087 & 0.086 & 0.079 \\  Residual Std. Error (df = 6201) & 11.670 & 11.675 & 11.549 \\  F Statistic (df = 32; 6201) & 19.453$^{***}$ & 19.247$^{***}$ & 17.720$^{***}$ \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular} 
} \end{frame}

@@

\begin{frame}   \frametitle{Future research - NBA}
  Within the NBA
  \begin{itemize}     
    \item Are teams more likely to party after a win or a       loss?
    \item Do teams who aren't going to make the playoffs party more?
    \item Are there demographic differences which influence propensity to party? E.g. are younger, unmarried players more susceptible to our treatment effect?
    \item We could also examine how shots taken vs. shots scored are affected for star players.
  \end{itemize}
  \vspace{12pt}  A preliminary and ad-hoc analysis shows that injury risk increases as a function of party.\footnote{We look for instances where players are put on the bench and stop playing (at least several) games as a function of our nightlife indicator.}
  This might inform coaches which players to bench and when.
\end{frame}
